### 2014-06-06 writing/S'14 paper/methods.tex
Methods error fix.

We study neural models that adhere to the linguistic \ii{principle of
 compositionality}, which says that the meanings for complex
expressions are derived from the meanings of their constituent parts
via specific combination functions \cite{Partee84,Janssen97}. In our
distributed setting, word meanings are vectors of length $N$. The
combination function concatenates pairs of them to form vectors of
length $2N$ and maps those larger vectors back into length $N$
vectors, which can then be merged again to create more complex
phrases. Once the entire sentence-level representation has been
derived, it is fed to a classifier trained in a supervised manner.

>>>>

We study neural models that adhere to the linguistic \ii{principle of
 compositionality}, which says that the meanings for complex
expressions are derived from the meanings of their constituent parts
via specific combination functions \cite{Partee84,Janssen97}. In our
distributed setting, word meanings are vectors of length $N$. The
combination function maps pairs of them to single vectors of length $N$
vectors, which can then be merged again to create more complex
phrases. Once the entire sentence-level representation has been
derived, it is fed to a classifier trained in a supervised manner.
